SPA: An Apache Spark Pilot scheduler\\ for HPC applications

### 2019-04-29 paper.tex
Comments on abstract and intro

\newcommand{\tristan}[1]{\color{red}\textbf{Note from Tristan}:
      #1 \color{black}}

@@

\begin{abstract}
    Big Data has become prominent throughout many scientific fields and, as a
    result, scientific communities have sought out Big Data frameworks to 
    accelerate the processing of their increasingly data-intensive pipelines.
    However, while scientific communities typically rely on High-Performance 
    Computing (HPC) clusters for the parallelization of their pipelines, many 
    popular Big Data frameworks such as Hadoop and Spark were primarily designed
    to be executed on dedicated commodity infrastructure. Differences found between
    these infrastructures and the policies that surround them limit the advantages
    of deploying Big Data pipelines on HPC infrastructure. For instance, HPC
    clusters typically employ a batch job submission system requiring users to
    specify details on number of cores, nodes, amount of memory and duration.
    Big Data engines, such as Spark, have no built-in mechanism to interact with
    HPC batch job submission systems. Morever, the details required by the HPC
    schedulers are not necessarily initially known to users of Big Data frameworks.

    Pilot scheduling strategies have been developed to address the limitations 
    of traditional HPC batch job schedulers. Pilot schedulers decouple resource
    provisioning from task scheduling, thereby enabling efficient resource
    utilization through dynamic scheduling. This paper evaluates the benefits 
    pilot-scheduling strategies over traditional batch submission
    on HPC clusters with overlay Apache Spark clusters. We first evaluate the
    overall speedup brought on by employing pilot-scheduling strategies. We then
    examine the robustness to master and driver failures, which may be frequent 
    when underestimating pilot walltime. Spark built-in checkpointing is also 
    investigated in relation to pilot expiration.

@@

In the recent years, neuroimaging Big Data has become more accessible, as a
result of the growing number of open-data initiatives~\cite{openneuro, hcp, ukbiobank}. However, the
processing of such large datasets using standard neuroimaging pipelines has 
become cumbersome. As a result, many researchers are moving towards Big Data 
engines, such as Apache Spark~\cite{spark} and Dask~\cite{sdask}, to 
create their processing pipelines. Unlike traditional neuroimaging 
engines, Big Data engines were designed to be executed on dedicated 
commodity infrastructures using Big Data schedulers. However, 
researchers still largely rely on High Performance Computing (HPC) 
infrastructure to process their data, although they may have access to 
clouds or local workstations.

@@

The recommended method for launching Spark applications on HPC schedulers 
involves batch requesting all the necessary resources and launching a standalone
Spark cluster once the resources have been requested. This could significantly increase
the scheduling time of Spark-based applications as a large amount of resources 
may be necessary to process Big Data. In a pilot-scheduling model, rather than requesting all the resources 
at once, a Spark cluster is launched with a subset of the resources and is expanded as 
more resources get allocated. This, in turn, may reduce the overall processing of
an application as less resources are requested at once and are therefore more likely
to be scheduled faster.

@@

>>>>

\newcommand{\tristan}[1]{\color{red}\textbf{Note from Tristan}:
      #1 \color{black}}
\newcommand{\TG}[1]{\tristan{#1}}

@@

\begin{abstract}
    Big Data has become prominent throughout many scientific fields and, as a
    result, scientific communities have sought out Big Data frameworks to 
    accelerate the processing of their increasingly data-intensive pipelines.
    \TG{I'd write the previous sentence in continuous present tense, since I think
    this is an on-going process.}
    However, while scientific communities typically rely on High-Performance 
    Computing (HPC) clusters for the parallelization of their pipelines, many 
    popular Big Data frameworks such as Hadoop and Spark were primarily designed
    to be executed on dedicated commodity infrastructures. Differences found between
    these infrastructures and the policies that surround them limit the advantages
    of deploying Big Data pipelines on HPC infrastructure. For instance, HPC
    clusters typically employ a batch job submission system requiring users to
    specify details on number of cores, nodes, amount of memory and duration.
    Big Data engines, such as Spark, have no built-in mechanism to interact with
    HPC batch job submission systems. Morever, the details required by the HPC
    schedulers \TG{be more specific than ``details'': do you mean ``scheduling policies'',
    ``application resource requirerments?''
    } are not necessarily initially known to users of Big Data frameworks.
    \TG{The previous paragraph is a bit long: it could be summarized to 2-3
    sentences.}

    Pilot scheduling strategies have been developed to address the limitations 
    of traditional HPC batch job schedulers \TG{You could give examples of pilot schedulers as you did with Spark and Hadoop}.
    Pilot schedulers decouple resource
    provisioning from task scheduling, thereby enabling efficient resource
    utilization through dynamic scheduling. This paper evaluates the benefits 
    pilot-scheduling strategies over traditional batch submission
    on HPC clusters with overlay Apache Spark clusters. We first evaluate the
    overall speedup brought on by employing pilot-scheduling strategies. We then
    examine the robustness to master and driver failures, which may be frequent 
    when underestimating pilot walltime. Spark built-in checkpointing is also 
    investigated in relation to pilot expiration.

@@

In the recent years, neuroimaging \TG{If you want to put neuroimaging first, then you need to explain it. Just say that it's an example among many fields}
Big Data has become more accessible, as a
result of the growing number of open-data initiatives~\cite{openneuro, hcp, ukbiobank}. However, the
processing of such large datasets using standard neuroimaging pipelines has 
become cumbersome. As a result, many researchers are moving towards Big Data 
engines, such as Apache Spark~\cite{spark} and Dask~\cite{sdask}, to 
create their processing pipelines. Unlike traditional neuroimaging 
engines, Big Data engines were designed to be executed on dedicated 
commodity infrastructures using Big Data schedulers. However, 
researchers still largely rely on High Performance Computing (HPC) 
infrastructure to process their data, although they may have access to 
clouds or local workstations.

@@

The recommended method for launching Spark applications on HPC schedulers 
involves batch requesting all the necessary resources and launching a standalone
Spark cluster once the resources have been requested \TG{Add link to Compute Canada's instructions?}. This could significantly increase
the scheduling time of Spark-based applications as a large amount of resources 
may be necessary to process Big Data. In a pilot-scheduling model, rather than requesting all the resources 
at once, a Spark cluster is launched with a subset of the resources and is expanded as 
more resources get allocated. This, in turn, may reduce the overall processing of
an application as less resources are requested at once and are therefore more likely
to be scheduled faster.

@@

\TG{The introduction is still very much geared toward the presentation of 
the SPA software. Instead, I think it should introduce the question whether pilot jobs
are useful at all to overlay schedulers, explain why they may be, and why they may not (there is already an overlay scheduler,
and resource heterogeneity is limited). You could explain that the traditional benefits of pilot-job systems are:
\begin{itemize}
    \item Address worker node heterogeneity
    \item Address worker node failures (software, incl walltime expirations, or hardware)
    \item Address variable queuing times
    \item Tolerant to resource requirement overestimation, in particular walltime and CPU
    \item Increase workload distribution (use more nodes)
\end{itemize}
Among these, (1) and to some extent (2) are already addressed by an overlay scheduler.

The title should also reflect this.
}
